Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Improving some more with the help of ChatGPT

This inclusion of university-provided messaging applications in the survey might
explain why there are so few teachers, just 6.7\%, that answered they did not
use any messaging application. In general, universities provide official
channels to send students academic information such as the exam schedule or the
grades. The statistical mode is to use that kind of messaging. Some other
teaching staff might not use it, but use some extraofficial or opt-in channels
such as the others included in the survey; in the end, between these official
and extra-official channels, most people cover their needs to communicate with
students. This matches our subjective experience, in general.

Additionally, the question on COVID reflected the big challenge that represents
changing habits, even in the case of a major crisis. Very few responders
actually changed their habits, although comparing women vs. men as well as those
teaching social sciences show some significant differences. We do not have any
kind of explanation for this behavior, other than technologies are perceived,
and adopted, in a different way depending on background and, apparently, gender.

>>>>

This inclusion of university-provided messaging applications in the survey might
explain why there are so few teachers, just 6.7\%, that answered they did not
use any messaging application. In general, universities provide official
channels to send (or simply make available to) students academic information
such as the exam schedule or the grades. The statistical mode is to use that
kind of messaging. Some other teaching staff might not use it, but use some
extraofficial or opt-in channels such as the others included in the survey; in
the end, between these official and extra-official channels, most people cover
their needs to communicate with students. This matches the subjective experience
of the authors of this paper, in general.

Furthermore, the answers to the survey question regarding COVID highlights the
significant challenge of altering behavior, even during a major crisis. Very few
responders actually changed their habits, although comparing women vs. men as
well as those teaching social sciences vs. the rest of the disciplines, there
are some significant differences. We do not have any kind of explanation for
this behavior, other than technologies are perceived, and adopted, in a
different way depending on background and, apparently, gender.
